### 2014-11-01 thesis/results/overall-trauma-acc.tex
Update results and discussion section

\caption{Overall accuracy of each classifier with a particular feature selection method on the trauma data set. `D' indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied.}

@@

ZeroR & 66.91 & 66.91 & 66.91 & 66.91 & 66.91 & 66.91 & 66.91 & 66.91 \\
1R & 71.95 & 66.91 & \begin{tabular}[c]{@{}c@{}}70.64\\ D\end{tabular} & \textbf{72.01} & 71.93 & \begin{tabular}[c]{@{}c@{}}71.91\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.95\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.97\\ t=66.905\end{tabular} \\
NB & \begin{tabular}[c]{@{}c@{}}73.83\\ D\end{tabular} & 74.62 & \begin{tabular}[c]{@{}c@{}}73.19\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.4\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}75.8\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.85\\ D, t=0.125\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.45\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}72.37\\ D, t=69.905\end{tabular} \\
DT & \begin{tabular}[c]{@{}c@{}}75\\ D\end{tabular} & 74.38 & \begin{tabular}[c]{@{}c@{}}76.39\\ D\end{tabular} & 75.4 & \textbf{\begin{tabular}[c]{@{}c@{}}77.52\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}76.05\\ D, t=0.11\end{tabular} & \begin{tabular}[c]{@{}c@{}}76.17\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.49\\ t=66.905\end{tabular} \\
LR & \begin{tabular}[c]{@{}c@{}}77.62\\ D\end{tabular} & 75.06 & \begin{tabular}[c]{@{}c@{}}76.45\\ D\end{tabular} & 74.14 & \begin{tabular}[c]{@{}c@{}}76.3\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}77.7\\ D, t=0\end{tabular}} & \begin{tabular}[c]{@{}c@{}}77.65\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.4\\ D, t=66.905\end{tabular} \\
SVM & \begin{tabular}[c]{@{}c@{}}77.39\\ D\end{tabular} & 74.47 & \begin{tabular}[c]{@{}c@{}}75.67\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}72.57\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}75.26\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}77.42\\ D, t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}77.53\\ D, t=0.005\end{tabular}} & \begin{tabular}[c]{@{}c@{}}73.83\\ D, t=66.905\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}71.22\\ D\end{tabular} & 70.28 & \begin{tabular}[c]{@{}c@{}}72.56\\ D\end{tabular} & 74.44 & \textbf{\begin{tabular}[c]{@{}c@{}}77.81\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.75\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.26\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.78\\ t=68.905\end{tabular} \\
20NN & \begin{tabular}[c]{@{}c@{}}75.9\\ D\end{tabular} & 73.59 & \begin{tabular}[c]{@{}c@{}}75.51\\ D\end{tabular} & 75.3 & \begin{tabular}[c]{@{}c@{}}76.48\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}76.26\\ D, t=0.125\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}76.56\\ D, t=0.005\end{tabular}} & \begin{tabular}[c]{@{}c@{}}73.56\\ t=68.905\end{tabular} \\
RD & \begin{tabular}[c]{@{}c@{}}76.92\\ D\end{tabular} & 69.68 & \begin{tabular}[c]{@{}c@{}}76.19\\ D\end{tabular} & 74.38 & \textbf{\begin{tabular}[c]{@{}c@{}}77.22\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}76.87\\ D, t=0.05\end{tabular} & \begin{tabular}[c]{@{}c@{}}76.82\\ D, t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.83\\ D, t=66.905\end{tabular} \\
K* & \begin{tabular}[c]{@{}c@{}}71.4\\ D\end{tabular} & 72.20 & \begin{tabular}[c]{@{}c@{}}75.08\\ D\end{tabular} & 75.58 & \textbf{\begin{tabular}[c]{@{}c@{}}77.27\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}75.07\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.08\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.45\\ t=68.905\end{tabular} \\
MLP & \begin{tabular}[c]{@{}c@{}}73.79\\ D\end{tabular} & 73.03 & \begin{tabular}[c]{@{}c@{}}73.45\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.38\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}76.66\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.65\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.03\\ D, t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.94\\ D, t=66.905\end{tabular} \\ \hline

>>>>

\label{tab:overall-tr-acc}
\caption{Overall best accuracy of each classifier with a particular feature selection method on the trauma data set. * indicates that results were identical regardless of discretisation. D indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied. The absence of * or D means that not discretising produced a better result. The best result for each classifier is highlighted in bold, with ties broken in favour of the smallest feature set.}

@@

ZeroR & 66.91* & 66.91* & 66.91* & 66.91* & 66.91* & 66.91* & 66.91* & 66.91* \\
1R & 71.95 & 66.91* & \begin{tabular}[c]{@{}c@{}}70.64\\ D\end{tabular} & \textbf{72.01} & 71.93 & \begin{tabular}[c]{@{}c@{}}71.91\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.95\\ t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.97\\ t=66.905\end{tabular} \\
NB & \begin{tabular}[c]{@{}c@{}}73.83\\ D\end{tabular} & 74.62* & \begin{tabular}[c]{@{}c@{}}73.19\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.4\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}75.8\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.85\\ D, t=0.125\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.45\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}72.37\\ D, t=69.905\end{tabular} \\
DT & \begin{tabular}[c]{@{}c@{}}75\\ D\end{tabular} & 74.38* & \begin{tabular}[c]{@{}c@{}}76.39\\ D\end{tabular} & 75.4 & \textbf{\begin{tabular}[c]{@{}c@{}}77.52\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}76.05\\ D, t=0.11\end{tabular} & \begin{tabular}[c]{@{}c@{}}76.17\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.49\\ t=66.905\end{tabular} \\
LR & \begin{tabular}[c]{@{}c@{}}77.62\\ D\end{tabular} & 75.06* & \begin{tabular}[c]{@{}c@{}}76.45\\ D\end{tabular} & 74.14 & \begin{tabular}[c]{@{}c@{}}76.3\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}77.7\\ D, t=0\end{tabular}} & \begin{tabular}[c]{@{}c@{}}77.65\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.4\\ D, t=66.905\end{tabular} \\
SVM & \begin{tabular}[c]{@{}c@{}}77.39\\ D\end{tabular} & 74.47* & \begin{tabular}[c]{@{}c@{}}75.67\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}72.57\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}75.26\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}77.42\\ D, t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}77.53\\ D, t=0.005\end{tabular}} & \begin{tabular}[c]{@{}c@{}}73.83\\ D, t=66.905\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}71.22\\ D\end{tabular} & 70.28* & \begin{tabular}[c]{@{}c@{}}72.56\\ D\end{tabular} & 74.44 & \textbf{\begin{tabular}[c]{@{}c@{}}77.81\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.75\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.26\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.78\\ t=68.905\end{tabular} \\
20NN & \begin{tabular}[c]{@{}c@{}}75.9\\ D\end{tabular} & 73.59* & \begin{tabular}[c]{@{}c@{}}75.51\\ D\end{tabular} & 75.3 & \begin{tabular}[c]{@{}c@{}}76.48\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}76.26\\ D, t=0.125\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}76.56\\ D, t=0.005\end{tabular}} & \begin{tabular}[c]{@{}c@{}}73.56\\ t=68.905\end{tabular} \\
RD & \begin{tabular}[c]{@{}c@{}}76.92\\ D\end{tabular} & 69.68* & \begin{tabular}[c]{@{}c@{}}76.19\\ D\end{tabular} & 74.38 & \textbf{\begin{tabular}[c]{@{}c@{}}77.22\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}76.87\\ D, t=0.05\end{tabular} & \begin{tabular}[c]{@{}c@{}}76.82\\ D, t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.83\\ D, t=66.905\end{tabular} \\
K* & \begin{tabular}[c]{@{}c@{}}71.4\\ D\end{tabular} & 72.20* & \begin{tabular}[c]{@{}c@{}}75.08\\ D\end{tabular} & 75.58 & \textbf{\begin{tabular}[c]{@{}c@{}}77.27\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}75.07\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.08\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.45\\ t=68.905\end{tabular} \\
MLP & \begin{tabular}[c]{@{}c@{}}73.79\\ D\end{tabular} & 73.03* & \begin{tabular}[c]{@{}c@{}}73.45\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}73.38\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}76.66\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}74.65\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}74.03\\ D, t=0.001\end{tabular} & \begin{tabular}[c]{@{}c@{}}71.94\\ D, t=66.905\end{tabular} \\ \hline

### 2014-11-01 thesis/results/overall-trauma-auc.tex
Update results and discussion section

\caption{Overall AUC performance of each classifier with a particular feature selection method on the trauma data set. `D' indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied.}

@@

ZeroR & 0.498 & 0.498 & 0.498 & 0.498 & 0.498 & 0.498 & 0.498 & 0.498 \\
1R & 0.67 & 0.5 & \begin{tabular}[c]{@{}c@{}}0.581\\ D\end{tabular} & 0.668 & 0.668 & \begin{tabular}[c]{@{}c@{}}0.669\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.669\\ t=0.005\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.67\\ t=69.905\end{tabular}} \\
NB & \begin{tabular}[c]{@{}c@{}}0.828\\ D\end{tabular} & 0.804 & \begin{tabular}[c]{@{}c@{}}0.806\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.815\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.827\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.829\\ D, t=0.125\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.832\\ D, t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.8\\ D, t=66.905\end{tabular} \\
DT & \begin{tabular}[c]{@{}c@{}}0.756\\ D\end{tabular} & 0.772 & \begin{tabular}[c]{@{}c@{}}0.786\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.793\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.806\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.799\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.787\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.766\\ D, t=66.905\end{tabular} \\
LR & \begin{tabular}[c]{@{}c@{}}0.844\\ D\end{tabular} & 0.812 & \begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.819\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.831\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.846\\ D, t=0.1\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.844\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.811\\ D, t=66.905\end{tabular} \\
SVM & \begin{tabular}[c]{@{}c@{}}0.843\\ D\end{tabular} & 0.787 & 0.807 & \begin{tabular}[c]{@{}c@{}}0.782\\ D\end{tabular} & 0.806 & \textbf{\begin{tabular}[c]{@{}c@{}}0.844\\ D, t=0.1\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.842\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.724\\ D, t=66.905\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}0.726\\ D\end{tabular} & 0.719 & \begin{tabular}[c]{@{}c@{}}0.760\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.798\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.816\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.798\\ D, t=0.2\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.768\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.778\\ t=68.905\end{tabular} \\
20NN & \begin{tabular}[c]{@{}c@{}}0.827\\ D\end{tabular} & 0.792 & \begin{tabular}[c]{@{}c@{}}0.808\\ D\end{tabular} & 0.814 & \begin{tabular}[c]{@{}c@{}}0.828\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.831\\ D, t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.832\\ D, t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.799\\ D, t=66.905\end{tabular} \\
RD & \begin{tabular}[c]{@{}c@{}}0.834\\ D\end{tabular} & 0.742 & \begin{tabular}[c]{@{}c@{}}0.807\\ D\end{tabular} & 0.81 & \begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.836\\ D, t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.834\\ D, t=0.005\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.791\\ D, t=66.905\end{tabular} \\
K* & \begin{tabular}[c]{@{}c@{}}0.768\\ D\end{tabular} & 0.774 & \begin{tabular}[c]{@{}c@{}}0.803\\ D\end{tabular} & 0.815 & \textbf{\begin{tabular}[c]{@{}c@{}}0.838\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.82\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.802\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.787\\ t=68.905\end{tabular} \\
MLP & \begin{tabular}[c]{@{}c@{}}0.803\\ D\end{tabular} & 0.781 & \begin{tabular}[c]{@{}c@{}}0.784\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.802\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.818\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.803\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.772\\ D, t=68.905\end{tabular} \\ \hline

>>>>

\label{tab:overall-tr-auc}
\caption{Overall best AUC of each classifier with a particular feature selection method on the trauma data set. * indicates that results were identical regardless of discretisation. D indicates that discretisation was used, and $t$ is the threshold at which the feature selector was applied. The absence of * or D means that not discretising produced a better result. The best result for each classifier is highlighted in bold, with ties broken in favour of the smallest feature set.}

@@

ZeroR & 0.498* & 0.498* & 0.498* & 0.498* & 0.498* & 0.498* & 0.498* & 0.498* \\
1R & 0.67 & 0.5* & 0.581* & 0.668 & 0.668 & \begin{tabular}[c]{@{}c@{}}0.669\\ t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.669\\ t=0.005\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.67\\ t=69.905\end{tabular}} \\
NB & \begin{tabular}[c]{@{}c@{}}0.828\\ D\end{tabular} & 0.804* & \begin{tabular}[c]{@{}c@{}}0.806\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.815\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.827\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.829\\ D, t=0.125\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.832\\ D, t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.8\\ D, t=66.905\end{tabular} \\
DT & \begin{tabular}[c]{@{}c@{}}0.756\\ D\end{tabular} & 0.772* & \begin{tabular}[c]{@{}c@{}}0.786\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.793\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.806\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.799\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.787\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.766\\ D, t=66.905\end{tabular} \\
LR & \begin{tabular}[c]{@{}c@{}}0.844\\ D\end{tabular} & 0.812* & \begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.819\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.831\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.846\\ D, t=0.1\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.844\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.811\\ D, t=66.905\end{tabular} \\
SVM & \begin{tabular}[c]{@{}c@{}}0.843\\ D\end{tabular} & 0.787* & 0.807 & \begin{tabular}[c]{@{}c@{}}0.782\\ D\end{tabular} & 0.806 & \textbf{\begin{tabular}[c]{@{}c@{}}0.844\\ D, t=0.1\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.842\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.724\\ D, t=66.905\end{tabular} \\
1NN & \begin{tabular}[c]{@{}c@{}}0.726\\ D\end{tabular} & 0.719* & \begin{tabular}[c]{@{}c@{}}0.760\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.798\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.816\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.798\\ D, t=0.2\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.768\\ t=0.1\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.778\\ t=68.905\end{tabular} \\
20NN & \begin{tabular}[c]{@{}c@{}}0.827\\ D\end{tabular} & 0.792* & \begin{tabular}[c]{@{}c@{}}0.808\\ D\end{tabular} & 0.814 & \begin{tabular}[c]{@{}c@{}}0.828\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.831\\ D, t=0.1\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.832\\ D, t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.799\\ D, t=66.905\end{tabular} \\
RD & \begin{tabular}[c]{@{}c@{}}0.834\\ D\end{tabular} & 0.742* & \begin{tabular}[c]{@{}c@{}}0.807\\ D\end{tabular} & 0.81 & \begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.836\\ D, t=0.01\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.834\\ D, t=0.005\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.791\\ D, t=66.905\end{tabular} \\
K* & \begin{tabular}[c]{@{}c@{}}0.768\\ D\end{tabular} & 0.774* & \begin{tabular}[c]{@{}c@{}}0.803\\ D\end{tabular} & 0.815 & \textbf{\begin{tabular}[c]{@{}c@{}}0.838\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.82\\ D, t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.802\\ D, t=0.01\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.787\\ t=68.905\end{tabular} \\
MLP & \begin{tabular}[c]{@{}c@{}}0.803\\ D\end{tabular} & 0.781* & \begin{tabular}[c]{@{}c@{}}0.784\\ D\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.802\\ D\end{tabular} & \textbf{\begin{tabular}[c]{@{}c@{}}0.825\\ D\end{tabular}} & \begin{tabular}[c]{@{}c@{}}0.818\\ t=0.15\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.803\\ D, t=0\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.772\\ D, t=68.905\end{tabular} \\ \hline
